### 2013-03-19 drafts/general_writeup/writeup.tex
Reorganization and cleanup of drafts directory.

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

@@

@@

@@

\bibliographystyle{plain}
\bibliography{bibliography}

>>>>

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath}

@@

\DeclareMathOperator*{\argmax}{arg\,max}

@@

\section{Algorithm 0}
In order to motivate our approach, we present the following problem:
suppose we have a probability model $P(D, E, \mathcal{L}) = P(D|E)
P(E|L) P(L)$ where $L$ represents the parameters of a latent model,
$E_i$ are drawn $i.i.d$ from $P(\dot | L)$ and $D_i$ are drawn $i.i.d$
from $P(\dot|E_i)$. The $E_i$ are hidden, the $D_i$ observed. Suppose
we are able to 1) draw sampled of $E_i$ given $L$ and 1) we can
enumerate $E_i$ in order of decreasing probability under $L$. Our goal
is to determine the most likely $L$ given the data $D$. A rejection
sampling algorithm approach might involve sampling the $E_i$ from the
current value of $L$, accepting $E_i$ if  To solve this problem, we propose
Algorithm~\ref{alg:short}: at each iteration of our algorithm, we
choose

\begin{minipage}{.7\linewidth}
  \begin{algorithm}[H]
    \SetAlgoLined 
    \KwData{$\mathcal{D}=(D_1, \dots, D_M)$,
      $\mathcal{L}^{t-1}$ , $0 \geq K \leq 1$} 
    \KwResult{updated library $\mathcal{L}^t$}
    $E \leftarrow \{ E_i : p(E_i\, |\, \mathcal{L}^{t-1}) > K\}$\;
    $S \leftarrow \{ h \in H \cap D \}$\;
    $\mathcal{L}^t \leftarrow \argmax_L p(L \, | \, S)$
    \caption{Algorithm 0}
    \label{alg:short}
  \end{algorithm}
\end{minipage}

@@

\bibliographystyle{plain}
\bibliography{writeup}
